\starttext
\setupbodyfont[sansserif, 10pt]
\setuppagenumbering [location=]

\title{SoMono LFNoise}

\SetTableToWidth{\textwidth}

LFNoise is a controller machine that is inspired by the SuperCollider
UGen off the same name. It generates a new random value once every
number of rows the number being specified by an appropriate parameter
of the machine. The value this machine outputs is one that is
interpolated between two adjacent random values by a chosen
interpolation method. There are three methods of interpolation
implemented: None, Linear and Cubic. None simply outputs a random
value when it is generated. Linear attempts to draw a straight line
between two adjacent values. Cubic draws a smooth curve and uses four
points for interpolation. You can also specify how the ouput of this
machine is scaled through Min and Max parameters. Suppose the output
after interpolation is $x$, the machine outputs $Min + x \times (Max -
Min)$. You can use LFNoise to create random fluctuations in parameter
values of other machines thus adding life and a random element to
your sounds. Just connect it to whatever you want to slowly change in
an unpredicted way over time.

\starttable[|l|l|l|l|p50|]
  \HL
  \NC \bf Parameter \NC \bf Min \NC \bf Max \NC \bf Units \NC \bf Meaning \NC \AR
  \HL
  \NC Rate \NC 1 \NC 128 \NC Rows \NC A new random value will be generate every this value rows. \NC \AR
  \NC Type \NC - \NC - \NC - \NC Choose an interpolation method from None, Linear or Cubic. \NC \AR
  \NC Min \NC 0.0 \NC 1.0 \NC Float \NC Minimum value the output can reach. \NC \AR
  \NC Max \NC 0.0 \NC 1.0 \NC Float \NC Maximum value the output can reach. \NC \AR
  \HL
\stoptable

\stoptext
