\starttext
\setupbodyfont[sansserif, 10pt]
\setuppagenumbering [location=]

\title{SoMono Control}

\SetTableToWidth{\textwidth}

Control is a controller bank. It can be used to control multiple
parameters on multiple machines (up to 8 different parameters). Simply
drag and drop from the appropriate control output to the slider you
want to control. The intended use for this machine is to have a single
machine that you can assign MIDI controller knobs to and control many
aspects of your song while only having to insert a single long pattern
in the sequencer view. I use it this way - compose a song or simply
decide how long it will be, make a Control pattern slightly longer
than that, assign MIDI controller knobs to the ``Value'' sliders in
the machine, add said pattern to the sequencer view, assign outputs to
parameters of other machines that I want to control, press record,
twiddle the knobs, repeat until results are satisfactory.

\placetable{none}{
\starttable[|l|l|l|l|p50|]
  \HL                   
  \NC \bf Parameter \NC \bf Min \NC \bf Max \NC \bf Units \NC \bf Meaning \NC \AR
  \HL
  \NC Value \NC 0.0 \NC 1.0 \NC Float \NC Slider value, before any
  post processing. \NC \AR
  \NC Power \NC -5.0 \NC 5.0 \NC Float \NC Apply non-linear
  processing to the slider value of specified strength. \NC \AR
  \NC Min \NC 0.0 \NC 1.0 \NC Float \NC Minimum value the output can reach. \NC \AR
  \NC Max \NC 0.0 \NC 1.0 \NC Float \NC Maximum value the output can reach. \NC \AR
  \HL
\stoptable
}

\stoptext
